\section{Validation} \label{sec:val}
Show that users are satisfied with your product. 
You can also give a user manual here describing how to use your system (process of completion of different tasks using your system )
You can use some matrices (time, cost, resource etc.) to compare your system with the previous system.


After finalizing the system in accordance with the team's plan, we showed it to the students and teachers and asked them to test it out for themselves. We were fortunate in that we didn't spot any problems with the system when testing all of the functions using actual data. We conducted user surveys to get insight into their perceptions of the system, and we were offered some recommendations for future enhancements as a result. Our testers provided us with a wide variety of valuable insights, and the end result was pretty exciting. Students and teachers experienced less struggles as a result of the developed system as compared to the current system.

The basic differences we noted from the insights and thoughts of testers between the current system and our developed system is shown below.

\begin{itemize}

\item \textbf{Time}\\
Out of all the facts, our project's main concern was to reduce the time to perform the same operations. We have seen in the statistics that it costs 98 percent less time to submit the tuition fee through our system than current analog system. The time is optimized as students don't have to stand in a queue, bank officers don't have to attest the payments manually, and students can pay their fees anytime they wish.

\item \textbf{Efficiency}\\
The newly developed system is highly efficient than previous system. Authority has expressed their satisfaction with the system as they don't have to calculate data manually anymore in case they use this system. This system is proven to be better as there are almost zero percentage chance to be unsuccessful to submit the on due time.

\item \textbf{Cashless}\\
Moving with the digital world, this system introduces the university with a cashless payment system.

\item \textbf{Independence}\\
The system only depends on an online payment gateway to perform the transaction which allows users to make payment through any medium such as bank, mobile bank etc. In this way the university will get rid of dependency on specific bank branch. As the current system fully depends on the bank branch, it also depends on a certain period of whole daytime that is working period of the bank. But in our system, there are no chances to depend on any specific time period. One can pay fees any time they wish.\\
Student and administrations don't have to be present physically to complete transactions anymore. In our system, both students and administrations can perform tasks from anywhere just using the internet.

\item \textbf{Time saving with attendance system}\\
It has been seen that teachers can now save 25 to 30 percentage of the class session if they start attesting attendance through our system. It not only saves time but also reduce the discomfort of taking attendance of teachers. Students were seemed happy to use the new attendance system.

\item \textbf{Data Analysis}\\
In current system, administrations need to calculate several data manually which costs a good amount of time and mental work. But in our proposed system, those data are automatically generated by the system and also represented graphically which will help authority to reduce the difficulties to make decisions. It should be noted that, in current system, calculations can go wrong as it requires more people to complete.


\end{itemize}

Since a vast number of users expressed the satisfaction with the developed system, administrations may take necessary decisions to replace the current system with the new one.
 
\clearpage